Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-31 paper.tex
Streamline intro a bit

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Scaled models have the benefit of being significantly less expensive, however,
there still is concern at which scale an experiment must be performed to be
relevant to full-scale application. This is particularly important for
cross-flow turbines, where Reynolds number effects for experiments conducted at
low $Re$ are often difficult to distinguish from the effects on performance of
several other turbine parameters.

If numerical models are validated with physical model data that was obtained at
insufficiently high Reynolds numbers, it cannot be determined whether problems
with model predictions matching full scale observations are caused by Reynolds
number effects or issues with the numerical model itself. One might also obtain
different predictions for scaled systems due to modified physics at lower
Reynolds numbers, e.g., laminar boundary layers and transitional flow regimes.
If the numerical model is then considered ``validated,'' there is a risk that
its application at full-scale may produce incorrect predictions. As such, it is
questionable whether numerical models validated with physical model data
obtained at Reynolds numbers orders of magnitude away from prototype scale
should be considered validated at all.

>>>>

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Scaled models have the benefit of being significantly less expensive, however,
there still is concern at which scale an experiment must be performed to be
relevant to full-scale application. One might obtain different predictions for
scaled systems due to modified physics at lower Reynolds numbers, e.g., laminar
boundary layers and transitional flow regimes. If the numerical model is then
considered ``validated,'' there is a risk that its application at full-scale may
produce incorrect predictions. As such, it is questionable whether numerical
models validated with physical model data obtained at Reynolds numbers orders of
magnitude away from prototype scale should be considered validated at all.
